% FortySecondsCV LaTeX template
% Copyright © 2019 René Wirnata <rene.wirnata@pandascience.net>
% Licensed under the 3-Clause BSD License. See LICENSE file for details.
%
% Attributions
% ------------
% * fortysecondscv is based on the twentysecondcv class by Carmine Spagnuolo
%   (cspagnuolo@unisa.it), released under the MIT license and available under
%   https://github.com/spagnuolocarmine/TwentySecondsCurriculumVitae-LaTex
% * further attributions are indicated immediately before corresponding code

%-------------------------------------------------------------------------------
%                             ADDITIONAL PACKAGES
%-------------------------------------------------------------------------------
\documentclass[
  a4paper,
%   showframes,
   maincolor=cvblue,
   sectioncolor=cvblue,
%  subsectioncolor  =orange
   sidebarwidth=0.323\paperwidth,
%   topbottommargin=0.03\paperheight,
%   leftrightmargin=20pt
]{fortysecondscv}

% improve word spacing and hyphenation
\usepackage{microtype}
\usepackage{ragged2e}
\usepackage{rotating}
\usepackage{enumitem}


% take care of proper font encoding
\ifxetex
	\usepackage{fontspec}
	\defaultfontfeatures{Ligatures=TeX}
% \newfontfamily\headingfont[Path = fonts/]{segoeuib.ttf} % local font
\else
	\usepackage[utf8]{inputenc}
	\usepackage[T1]{fontenc}
% \usepackage[sfdefault]{noto} % use noto google font
\fi

% enable mathematical syntax for some symbols like \varnothing
\usepackage{amssymb}

% bubble diagram configuration
\usepackage{smartdiagram}
\smartdiagramset{
  % defaut font size is \large, so adjust to harmonize with sidebar layout
  bubble center node font = \footnotesize,
  bubble node font = \footnotesize,
  % default: 4cm/2.5cm; make minimum diameter relative to sidebar size
  bubble center node size = 0.3\sidebartextwidth,
  bubble node size = 0.25\sidebartextwidth,
  distance center/other bubbles = 1.5em,
  % set center bubble color
  bubble center node color = maincolor!70,
  % define the list of colors usable in the diagram
  set color list = {maincolor!10, maincolor!40,
  maincolor!20, maincolor!60, maincolor!35},
  % sets the opacity at which the bubbles are shown
  bubble fill opacity = 0.8,
}


%-------------------------------------------------------------------------------
%                            PERSONAL INFORMATION
%-------------------------------------------------------------------------------
% profile picture
\cvprofilepic{pics/profile}
% your name
\cvname{\LARGE Hugo MACHEFER}
% job title/career
\cvjobtitle{Full Stack Developer  \\   | Devops | Tech Lead }

% phone number
\cvphone{001 514 659 0718}
% email address
\cvmail{hugo.machefer@gmail.com}

\cvlinkedin{linkedin.com/in/hugomachefer}{hugomachefer}

\cvgithub{https://github.com/hmachefe}{hugomachefer}

% short address/location, use \newline if more than 1 line is required
\cvaddress{Montréal, QC (Canada)}


% add additional information
% \newcommand{\additional}{some more?}


% add more profile sections to sidebar on first page
\addtofrontsidebar{
	% include gosquare national flags from https://github.com/gosquared/flags;
	% naming according to ISO 3166-1 alpha-2 country codes
	\graphicspath{{pics/flags/}}

  \vspace{-0.9mm}

	\profilesection{Skills}

  \vspace{-2.2mm}

    \chartlabel{Programmatic languages}\\
      \pointskillNinety{}{TypeScript, JavaScript}
      \pointskillNinety{}{HTML (HTML 5), CSS (3D)}
      \pointskillEighty{}{PHP (v7 et v5)}
      \pointskillSeventy{}{Python (v2 et v3)}
      \pointskillSeventy{}{C\# (.NET, Entity Framework)}
      \pointskillFifty{}{Java (Fx, Swing, Maven)}
      \pointskillFifty{}{Matlab}
      \pointskillFortyQt{}{C++ / C   (QT 5)}
    \chartlabel{Front-end (web)}\\
      \pointskillNinety{}{Angular (9/10/14/17.1)}
      \pointskillSeventy{}{React, jQuery}
      \pointskillEighty{}{RxJS / Observables}
      \pointskillEighty{}{Angular Material / PrimeNG}
      \pointskillSeventy{}{SCSS / SASS, Bootstrap}
      \pointskillSixty{}{Backbone, VueJS}
      \pointskillForty{}{ThreeJS (3D)}
      \pointskillSeventy{}{Electron}
    \chartlabel{Back-end}\\
      \pointskillNinety{}{OpenAPI/Swagger (TSOA)}
      \pointskillSeventy{}{Express, Node.js}
      \pointskillSixty{}{Microservices (in Python)}
      \pointskillSixty{}{Yii (PHP framework)}
      \pointskillSixty{}{Knex (Postgres, SQLite)}
      \pointskillForty{}{Django (Python framework)}
    \chartlabel{Database}\\
      \pointskillNinety{}{DynamoDB / (MongoDB)}
      \pointskillEighty{}{ElasticSearch}
      \pointskillSeventy{}{PostGres, Sqlite, MySql}
      \pointskillSeventy{}{MySQL Workbench, DBeaver}
      \pointskillForty{}{Microsoft SQL Server}
    \chartlabel{Protocol and security}\\
      \pointskillEighty{}{HTTP / HTTPS / SSL}
      \pointskillEighty{}{REST, GraphQL}
      \pointskillSixty{}{Auth0, Auth 2, JWT}
}


%-------------------------------------------------------------------------------
%                              SIDEBAR 2nd PAGE
%-------------------------------------------------------------------------------
\addtobacksidebar{
\vspace*{-3mm}  % Adjusts the vertical space, move content up by 10mm
\chartlabel{AWS Cloud}\\
\pointskillNinety{}{EC2, S3, CloudWatch}
\pointskillNinety{}{Lambdas (layer)}
\pointskillNinety{}{Secrets Manager}
\pointskillEighty{}{IAM, ECR, SES, SNS}
\pointskillEighty{}{CloudFront (CDN)}
\pointskillSeventy{}{Elastic Beanstalk}
\pointskillSeventy{}{Step Functions}
\pointskillTwenty{}{Fargate (ECS)}
\pointskillEighty{}{Route53 (DNS)}
\pointskillEighty{}{Certificates (ACM)}

\chartlabel{Azure Cloud}\\
\pointskillForty{}{Text To Speech Service}

\chartlabel{DevOps}\\
\pointskillEighty{}{Terraform (IaC Multi-Cloud)}
\pointskillSixty{}{Kubernetes (Orchestration)}
\pointskillFifty{}{CloudFormation (IaC AWS)}

\chartlabel{HTML5 players}\\
\pointskillNinety{}{Bitmovin}
\pointskillNinety{}{Accurate Player (Codemill)}
\pointskillSeventy{}{Video.js (open source)}

\chartlabel{Multimedia}\\
\pointskillNinety{}{ffmpeg, mediainfo, ffprobe}
\pointskillNinety{}{AWS MediaConvert}
\pointskillSeventy{}{Hybrik (Dolby)}

\chartlabel{Mobile Development}\\
\pointskillSixty{}{Java Android (Dalvik)}
\pointskillForty{}{Ionic (Apache Cordova)}
\pointskillThirty{}{Xcode (Objective C)}


\chartlabel{Version Control Systems}\\
\pointskillEighty{}{Git (gitlab, github)}
\pointskillForty{}{SVN / Synergy}

\chartlabel{Operating Systems}\\
\pointskillEighty{}{Linux (Ubuntu 22)}
\pointskillSeventy{}{Windows (Win 10)}
\pointskillSixty{}{MacOS (El Capitan 10.11.2)}
\pointskillSeventy{}{Tizen (Samsung TV)}
\pointskillForty{}{WebOS (LG TV)}


\chartlabel{IDE}\\
\pointskillEighty{}{Webstorm (Jetbrains)}
\pointskillEighty{}{Visual Code Editor}
\pointskillSeventy{}{Vim / Vi}


\chartlabel{Agility}\\
\pointskillEighty{}{Jira: backlog, sprint}
\pointskillEighty{}{Confluence / wiki}
\pointskillEighty{}{Scrum: grooming, review}

}

\addtothirdsidebar{
\vspace*{-8mm}  % Adjusts the vertical space, move content up by 10mm

  \chartlabel{Scripting}\\
  \pointskillEighty{}{Bash, shell (Linux, Mac)}
  \pointskillSeventy{}{CMD prompt, Powershell}

  \chartlabel{Streaming, DRM encryption}\\
  \pointskillEighty{}{MPEG/DASH, Widevine}
  \pointskillEighty{}{HLS, AES-128}

  \chartlabel{Instant messaging}\\
  \pointskillEighty{}{Teams, Slack}

  \chartlabel{UX / UI}\\
  \pointskillSeventy{}{Figma, Miro}

  \chartlabel{AI}\\
  \pointskillNinety{}{Chatgpt 4.0}
  \pointskillSixty{}{OpenAI API}

	\profilesection{Languages}
  \vspace{-1mm} % Adjust the negative space as needed
	\barskillLang{}{\textbf{French} (Mother Tongue)}{100}
	\barskillLang{}{\textbf{English} (TOEFL)}{92}
	\barskillLang{}{\textbf{German} (Educational, 2 years)}{35}
	\barskillLang{}{\textbf{Spanish} (Beginner, Duolingo)}{18}

	\profilesection{Honors \& awards}
    \vspace{-1mm} % Adjust the negative space as needed
		\skill{\faAward}{NDS CEO Award · Jan 2006}
		\skill{\faAward}{CSI Awards 2014}

  \profilesection{Teaching, Talks }
    \vspace{-1mm} % Adjust the negative space as needed
		\skill{\faChalkboardTeacher}{HTML5 coach (India, Israel, UK, US)}
    \skill{\faChalkboardTeacher}{Cross-cultural trainer, TMC}
		\skill{\faChalkboardTeacher}{ WebRTC (Intl dev conference, Berlin)}

  \vspace{-3mm} % Adjust the negative space as needed
	\profilesection{Education}
    \vspace{-1mm} % Adjust the negative space as needed
		\skill{\faLaptop}{Engineer's degree (ESEO) 1998}

	\profilesection{Interests}
    \vspace{-1mm} % Adjust the negative space as needed
		\skill{\faUnity}{WebGl/VR/AR, streaming, AI}
		\skill{\faGlobe}{International geopolitics}
		\skill{\faSwimmer}{Swimming, Basket-ball, Cycling}


	\profilesection{Short Bio}
  \vspace{-1mm} % Adjust the negative space as needed
	\aboutme{
    With more than 20 years in web development, I led various projects across digital TV and media platforms, enhancing software stacks with agile practices and technologies like AWS, Angular, Vue.js, React, PHP, Python, HTML5, and AI.
    }\\

}
%-------------------------------------------------------------------------------
%                         TABLE ENTRIES RIGHT COLUMN
%-------------------------------------------------------------------------------
\begin{document}


\newpage
\restoregeometry
\sidebarwidth=0.35\paperwidth

\makefrontsidebar

\vspace*{-3.7em} % Adjust the value as needed

\cvsection{Working Experience}


\begin{cvtableNew}


  \cvitemRightNew
    {Jan, 2025 – now} % Date
    {Senior Full-stack Developer Level 3} % Job title
    {Evident Scientific} % Company
    {
      \vspace{0.1pt} % Added space before "Role"
      \fontsize{10.8pt}{12pt}\selectfont % Subtle font increase
      \textbf{Role}: Full-stack borescope's inspection image app (cloud \& desktop)\vspace{4pt}
      \begin{itemize}[itemsep=-1mm, topsep=0pt, leftmargin=8pt]
        \item Frontend: HTML, SCSS, TypeScript, Angular 17+, RxJS, primeNg, Electron\vspace{5pt}
        \item Backend: C\#, .NET 8, JWT, Entity Framework SQL, Azure Blob Storage\vspace{5pt}
        \item Design and develop APIs and microservices as Azure Function App\vspace{5pt}
      \end{itemize}
    }
    {Montreal} % Location on the second line, aligned to the right

    \vspace{1.6mm} % Add vertical space after this entry


  \cvitemRightNew
      {Jan, 2020 – Nov, 2024} % Date
      {Full stack developer (and devops) | Tech lead} % Job title
      {difuze inc} % Company
      {
        \vspace{0.1pt} % Added space before "Role"
        \fontsize{10.8pt}{12pt}\selectfont % Subtle font increase
        \textbf{Role}: Similar to the mission at LVL Studio. Key projects include:\vspace{5pt}

        \begin{itemize}[itemsep=-1mm, topsep=0pt, leftmargin=8pt]
          \item \textbf{difuzego.com:} Angular 14 upgrade, MFA authentication implementation, assisted in migrating ElasticSearch data to PostgreSQL (Knex-compliant models). Built a file upload module using AWS Step Functions for compressed proxies. Enhanced workflows with on-prem Node.js workers (Express) and SQLite. Worked on MPEG/DASH encoding (AWS Mediaconvert, later Hybrik), HLS (AWS EC2 MacOS, later FFMPEG), and AES-128 encryption. Techs: CanvasJS, bandit, Bitmovin, VideoJs, Accurate Player, compression, encryption.\vspace{5pt}
          \item \textbf{difuzevox.com:} Integrated Azure Text-to-Speech and Auphonic API (mixing), local processing with ffmpeg, mediaInfo. Used ttml to generate voices, Video.js for multimedia. Managed Terraform infra. Led a team of 3 devs + 1 QA.\vspace{5pt}
          \item \textbf{AI Detection Project:} Developed solutions for detecting mouth shapes ("pucker"), scene changes, and burnt-in text using 3rd-party AI tools. Managed multi-window/browser communication (postMessage API).\vspace{5pt}
        \end{itemize}

        \textbf{CI/CD:} Contributed to Kubernetes-based deployments for on-prems projects.\vspace{5pt}

        \textbf{NPM Modules:} axios, knex, objection, pg, qrcode, speakeasy, srt2vtt, videojs...
      }
      {Montreal} % Location on the second line, aligned to the right

      \vspace{1.6mm} % Add vertical space after this entry



  \cvitemRightNew
    {Sep, 2017 – Jan, 2020} % Date
    {Full-Stack coder, Media Asset Management} % Job title
    {LVL Studio} % Company (without location here)
      {
        \vspace{0.2pt} % Add space before "Role"
        \fontsize{10.8pt}{12pt}\selectfont % Subtle font increase
        \textbf{Role}: As a key contributor to Difuze’s new software stack, I  helped shape the architecture and develop core modules for Difuze’s new stack. I also managed the Jira backlog, reviewed code via GitLab, and documented processes in Confluence for the B2B platform difuzego.com.\vspace{5pt}

        \vspace{0.1pt} % Add space before "Projects"
        \textbf{Projects:}
        \begin{itemize}[itemsep=1mm, topsep=5pt, leftmargin=8pt]
          \item \textbf{showcase.com}: Old legacy stack based on YII written in PHP, along with scripts in C\# for scheduling tasks like cron jobs. Side project: 15h of React.
          \item \textbf{difuzego.com}: New stack based on \textit{modern} AWS features written in TS.
        \end{itemize}

        \vspace{4pt} % Add space before "Purpose"
        \textbf{Purpose}: Development based on a Media Asset Management system accessed through HTTPS requests using SOAP protocol, enabling content display in catalog form, with the ability to share films as screeners, as promotional links in email, preceding deliveries as orders.\vspace{5pt}

        \textbf{Front-end}: Angular 2 (v7.2.9), RxJS, Angular Material, also including various NPM modules like ngx-translate, xml2js, ng2-file-upload, moment, socket.io etc\vspace{5pt}

        \textbf{Back-end}: RESTful services with OpenAPI, TypeScript Oriented Architecture (tsoa), NPM imports like exceljs, fs-extra, mustache, winston, user-
        agent etc\vspace{5pt}

        \textbf{Package Management}: Proficient with WebPack, Node.js, nvm, and yarn.\vspace{5pt}

        \textbf{Database and Search}: Managed both legacy (MySQL RDS) and new stack (DynamoDb, ElasticSearch).\vspace{5pt}

        \textbf{AWS DevOps}: Experience with ElasticBeanStalk, EC2, S3, Lambda layers, CloudWatch, IAM, ECR, SES, SNS, VPC. Infra deployed with Cloudformation.\vspace{5pt}

        \textbf{Additional Work}: Maintained legacy PHP/YII stack and MySQL RDS; minor C\# developments supervised over Mono on Ubuntu.\vspace{5pt}

        \textbf{Architecture}: Monolithic, no microservice. Data model shared between UI \& API. Common gitlab repository for front-end and back-end.\vspace{5pt}

        \textbf{CI/CD}: pipelines over gitlab including linter, prettier, unit tests + TDD, builder, ECR deployer, triggering Elastic Beanstalk's back-end environment update
      }
    {Montreal} % Location on the second line, aligned to the right
\end{cvtableNew}








\newpage
\makebacksidebar



\begin{cvtableNew}
  \cvitemRightNew
    {Jan, 2017 – June, 2017} % Date
    {Full Stack Developer in Healthcare Sector} % Job title
    {AlayaCare} % Company
    {
      \vspace{0.1pt} % Add space before "Role"
      \fontsize{10.8pt}{12pt}\selectfont % Subtle font increase
      \textbf{Role}: Developed web functionalities for healthcare platforms, full-stack.\par
      \vspace{4pt}
      \textbf{Front-end:} Created VUE.js components without jQuery, using libraries such as super-agent for AJAX requests, moment.js for date formatting, simple-vue-validator for validation, and LESS for optimized CSS. Creation of a new time-entry component tailored on jquery.timeentry plugin (out of VUE.js).\par
      \vspace{4pt}
      \textbf{Back-end:} Implemented PHP 5 solutions within the YII Framework, integrating the Carbon extension for enhanced date management, along with Python micro-services using SqlAlchemy. Ensured quality with precise unit tests and maintained accurate REST API documentation via APIARY.\par
      \vspace{4pt}
      \textbf{Mobile and Process Agility:} Conducted detailed Android code reviews and operated within a three-week sprint cycle, actively participating in standups, demos, retros, and grooming. Managed tasks and backlogs through Jira, with documentation centralized in Confluence.\par
      \vspace{4pt}
      \textbf{Virtualization:} Deployed µservices and software component as Dockerized\par
    }
    {Montreal} % Location on the second line, aligned to the right

\vspace{2.2mm} % Add vertical space after this entry

  \cvitemRightNew
    {May, 2015 – Dec, 2016} % Date
    {Front-End Developer in the Digital TV Sector} % Job title
    {Abbeal for Canal+} % Company
    {
      \vspace{-0.4pt} % Add space before "Role"
      \fontsize{10.8pt}{12pt}\selectfont % Subtle font increase
      \textbf{Role}: Developed and maintained WebApp interfaces and back-end for Canal+ digital TV receivers, reaching millions on TNT, SATELLITE, and IPTV.\par
      \vspace{4pt}
      \textbf{Front-End:} Developed HTML/CSS/JS UIs using ES2015 (Babel, Grunt), bundled with Webpack and rendered via Qt/WebKit on Linux; 10 h of React.\par
      \vspace{4pt}
      \textbf{Server-Side:} Supported by a Python UWSGI server hosting the WebApp and managing routing through DBUS for system interactions.\par
      \vspace{4pt}
      \textbf{Libraries and Frameworks:} Transitioned from BACKBONE to ANGULAR for enhanced MVC architecture; used LODASH for advanced data manipulation, EASELJS for interactive canvas operations, and EJS for templating.\par
      \vspace{4pt}
      \textbf{Agile and Testing:} Conducted unit tests with Mocha, Spy, and Sinon and API testing with Postman; managed agile sprints, tracked tasks in Jira, and documented outcomes in Confluence.\par
      \vspace{4pt}
      \textbf{Deployment:} Successfully deployed to 400,000 TNT receivers and subsequently expanded to over 2 million SAT subscribers globally.\par
      \vspace{4pt}
      \textbf{Nightwatch Project:} Led a Selenium-based task for UI navigation testing and REST API simulation, implemented on AWS EC2 with Docker.\par
      \vspace{4pt} % Ensures there is space after the last section before any text that might follow or end of the section.
    }
    {Paris (FR)} % Location on the second line, aligned to the right


    \vspace{1.18mm} % Add vertical space after this entry

  \cvitemRightNew
    {Dec, 2014 – Apr, 2015} % Date
    {Mobile and Backend Developer | Android \& NodeJS} % Job title
    {Cisco} % Company
    {
      \vspace{1pt} % Add space before "Project"
      \fontsize{10.8pt}{12pt}\selectfont % Subtle font increase
      \textbf{Project}: Integrated IoT with advanced TV for home automation.\par
      \vspace{4pt}
      \textbf{Technologies}: IoT using openHAB, Bluetooth (iBeacons), WiFi (Cisco MSE/Prime), RFID (Impinj). Enhanced TV channel personalization, ad targeting w/ Cisco analytics. Developed apps for wearables and Samsung mobiles, webSockets, Node.js servers.\par
      \vspace{4pt}
      \textbf{Ambilight \& UI}: Developed ambilight effects with GStreamer, matching Philips Hue lighting via Zigbee. Transitioned UI from Dart/WebGL to HTML/CSS on Cisco’s JUNO.\par
      \vspace{4pt}
      \textbf{Achievements}: Showcased at CES 2015, featured at Mobile World Congress, awarded \textit{Best IoT Product} by CSI Magazine.\par
      \vspace{4pt} % Ensures there is space after the last section before any text that might follow or end of the section.
    }
    {Paris (FR)} % Location on the second line, aligned to the right

    \vspace{1.16mm} % Add vertical space after this entry

    \cvitemRightNew
    {Aug, 2014 – Dec, 2014} % Date
    {Front-End developer | HTML \& JS | Digital TV apps} % Job title
    {Cisco} % Company
    {
      \vspace{1pt} % Add space before "Project"
      \fontsize{10.8pt}{12pt}\selectfont % Subtle font increase
      \textbf{Project}: Integrated IoT with advanced TV for home automa
      \textbf{Project}: Proof of concept WebApp for ZON TV Portugal.\par
      \vspace{4pt}
      \textbf{Technologies}: Vanilla JS, CSS3, HTML5 video player in custom UI manager to structure MVC views. Built core components such as the channel list, channel banner, EPG grid.\par
      \vspace{4pt}
      \textbf{Integration and Workflow}: Used QT on RDK middleware for optimized STB-to-backend data handling. Grunt (Node) and Jenkins for continuous integration, managing tasks through JIRA, and promoting effective teamwork in scrum.\par
      \vspace{4pt}
      \textbf{Outcome}: Successfully delivered a high-performance WebApp that improved user interaction between STB and ZON TV backend, showcased as an effective POC at major industry events.
    }
    {Paris (FR)} % Location on the second line, aligned to the right
\end{cvtableNew}











\newpage
\makethirdsidebar

\vspace*{-1em} % Adjust the value as needed
\begin{cvtableNew}
  \cvitemRightNew
    {Jan, 2014 – Jul, 2014} % Date
    {Interactive Front-End coder | BackboneJS \& ThreeJS} % Job title
    {Cisco} % Company
    {
      \vspace{1pt}
      \fontsize{10.8pt}{12pt}\selectfont % Subtle font increase
      \textbf{Project}: HTML5 application for Belgacom on RDK middleware; delivered high-performance POC with HW acceleration (GPU).\par
      \vspace{4pt}
      \textbf{Responsibilities}: app based on CSS3D and Three.JS part of BackboneJS views; with AJAX, WebSockets, Hammer.JS for tablet; packaged via PhoneGap.\par
    }
    {Paris (FR)} % Location on the second line, aligned to the right

    \vspace{1.57mm} % Add vertical space after this entry

  \cvitemRightNew
    {Mar, 2013 – Jan, 2014} % Date
    {Creative CSS3D/HTML5/JS for embedded devices } % Job title
    {NDS} % Company
    {
      \vspace{1pt}
      \fontsize{10.8pt}{12pt}\selectfont % Subtle font increase
      \textbf{Project}: HTML5 development for smart TVs, HDMI stick, Raspberry Pi, tablets.\par
      \vspace{4pt}
      \textbf{Responsibilities}: Built features with HTML5, CSS3D, WebGL, BackboneJS, ThreeJS (Collada), Tween.js.
      Optimized HW performance for QT5/WebKit, WebKitNix, Chromium. Cross-compiled web engines and gstreamers to target LG TVs,
      Raspberry Pi, Cotton Candy, MacOS rendering the same webapp.\par
      \vspace{4pt}
      \textbf{Outcome}: Delivered high-performance solutions attracting Belgacom \& Zon TV.\par
    }
    {Paris (FR)} % Location on the second line, aligned to the right

    \vspace{1.57mm} % Add vertical space after this entry

  \cvitemRightNew
    {Aug, 2012 – Feb, 2013} % Date
    {Front-End | AngularJS \& Backbone | Digital TV} % Job title
    {Cisco (ex NDS)} % Company
    {
      \vspace{1pt}
      \fontsize{10.8pt}{12pt}\selectfont % Subtle font increase
      \textbf{Project}: HTML5 solution for digital TV with patented remote UI, 2nd-screen.\par
      \vspace{4pt}
      \textbf{Responsibilities}: Developed on a patented HTML5 rendering solution for payTV, showcased @IBC. Evaluated how new generation of frameworks: Angular, Backbone, Spine, Google key controler behave on STB with benchmarks. Built MVC architecture for STB apps, assessed Flash-to-Html5 (e.g Adobe Edge).\par
      \vspace{4pt}
      \textbf{Skills}: HTML5 Development, Frameworks evaluation, MVC Architecture, Open-Source tools (GIT, Jira, Jenkins, Confluence).\par
    }
    {Paris (FR)} % Location on the second line, aligned to the right

    \vspace{1.57mm} % Add vertical space after this entry

  \cvitemRightNew
    {Dec, 2010 – Jul, 2012} % Date
    {Embedded Systems Developer | WebKit/QT \& HTML5} % Job title
    {NDS} % Company
    {
      \vspace{1pt}
      \fontsize{10.8pt}{12pt}\selectfont % Subtle font increase
      \textbf{Project}: QT/WebKit integration on specialized chips, performance, compliance.\par
      \vspace{4pt}
      \textbf{Responsibilities}: Cross-compiled QT/WebKit for various STB chipsets, developed Java-QT bridges for QWebView (Android, Qt). Automated binary distribution via shell (IN, IL), packaged HTML5 as .CRX for corporate app store.\par
    }
    {Paris (FR)} % Location on the second line, aligned to the right

    \vspace{1.57mm} % Add vertical space after this entry

  \cvitemRightNew
  {Feb, 2002 – Nov, 2010} % Date
  {Web Engine Integration, HTML widgets coder} % Job title
  {Canal+} % Company
  {
    \vspace{1pt}
    \fontsize{10.8pt}{12pt}\selectfont % Subtle font increase
    \textbf{Projects}:
    - Integrated Opera 6 then NetFront web engines into STBs, enabling advanced digital TV functionality. Cross-Department collaboration, worlwide. \par
    \vspace{4pt}
    \textbf{Responsibilities}:
    Led NDS/ACCESS collaboration for STB middleware integration, bindings to file system, memory manager, graphic stack, network interface, ssl,
    cross-platform porting.
    Developed Java-Opera and Java-QT bridges for custom plugins like Netscape, for seamless integration, multimedia playback.
    Additionnaly, built frameworks for STB games, modernized HTML standards, conducting performance optimization for multiple platforms.
    Creation of a bank of widgets, TV-oriented, STB-to-iPhone interaction, social networks (Facebook)

    \par
    \vspace{4pt}
    \textbf{Skills}: browser integration. C/C++, Java. HTML, CSS, JS. HBBTV, CE-HTML\par
  }
    {Paris (FR)} % Location on the second line, aligned to the right

    \vspace{1.57mm} % Add vertical space after this entry

  \cvitemRightNew
    {Sep, 1999 – Dec, 2001} % Date
    {Pay-TV System Integrator, Content Delivery Network} % Job title
    {Canal+} % Company
    {
      \vspace{1pt}
      \fontsize{10.8pt}{12pt}\selectfont % Subtle font increase
      \textbf{Project}: System integration and testing for Canal+ global multimedia platforms.\par
      \vspace{4pt}
      \textbf{Responsibilities}: Developed test scripts, managed end-to-end HW/SW integration, and provided on-site (Sacramento, USA) and remote support for Spain, Netherland, Japan.\par
      \vspace{4pt}
      \textbf{Skills}: Digital TV standards: DVB, MHP. Broadcasting: DVB-C, DVB-S, DVB-T.\par
    }
    {Paris (FR)} % Location on the second line, aligned to the right

    \vspace{1.87mm} % Add vertical space after this entry

    \cvitemRightNew
    {Oct, 1998 – Aug, 1999} % Date
    {DSP Engineer | Acoustic Echo Cancellation} % Job title
    {ALTEN} % Company
    {
      \vspace{1pt}
      \fontsize{10.8pt}{12pt}\selectfont % Subtle font increase
      \textbf{Project}: Spearheaded the development of Acoustic Echo Cancellation (AEC) solutions, enhancing audio clarity and speakerphone functionality in mobile devices, using advanced MATLAB and C++ techniques.\par
      \vspace{3.6pt}
      \textbf{Responsibilities}: Tuned AEC algorithms for echo suppression, noise reduction
      . Simulated and tested hands-free calls using a Visual C++
      executable.
    }
    {Issy Les Moulineaux (FR)} % Location on the second line, aligned to the right


\end{cvtableNew}




\end{document}
