% FortySecondsCV LaTeX template
% Copyright © 2019 René Wirnata <rene.wirnata@pandascience.net>
% Licensed under the 3-Clause BSD License. See LICENSE file for details.
%
% Attributions
% ------------
% * fortysecondscv is based on the twentysecondcv class by Carmine Spagnuolo
%   (cspagnuolo@unisa.it), released under the MIT license and available under
%   https://github.com/spagnuolocarmine/TwentySecondsCurriculumVitae-LaTex
% * further attributions are indicated immediately before corresponding code

%-------------------------------------------------------------------------------
%                             ADDITIONAL PACKAGES
%-------------------------------------------------------------------------------
\documentclass[
  a4paper,
%   showframes,
   maincolor=cvblue,
   sectioncolor=cvblue,
%  subsectioncolor  =orange
%   sidebarwidth=0.4\paperwidth,
%   topbottommargin=0.03\paperheight,
%   leftrightmargin=20pt
]{fortysecondscv}

% improve word spacing and hyphenation
\usepackage{microtype}
\usepackage{ragged2e}
\usepackage{rotating}

% take care of proper font encoding
\ifxetex
	\usepackage{fontspec}
	\defaultfontfeatures{Ligatures=TeX}
% \newfontfamily\headingfont[Path = fonts/]{segoeuib.ttf} % local font
\else
	\usepackage[utf8]{inputenc}
	\usepackage[T1]{fontenc}
% \usepackage[sfdefault]{noto} % use noto google font
\fi

% enable mathematical syntax for some symbols like \varnothing
\usepackage{amssymb}

% bubble diagram configuration
\usepackage{smartdiagram}
\smartdiagramset{
  % defaut font size is \large, so adjust to harmonize with sidebar layout
  bubble center node font = \footnotesize,
  bubble node font = \footnotesize,
  % default: 4cm/2.5cm; make minimum diameter relative to sidebar size
  bubble center node size = 0.3\sidebartextwidth,
  bubble node size = 0.25\sidebartextwidth,
  distance center/other bubbles = 1.5em,
  % set center bubble color
  bubble center node color = maincolor!70,
  % define the list of colors usable in the diagram
  set color list = {maincolor!10, maincolor!40,
  maincolor!20, maincolor!60, maincolor!35},
  % sets the opacity at which the bubbles are shown
  bubble fill opacity = 0.8,
}


%-------------------------------------------------------------------------------
%                            PERSONAL INFORMATION
%-------------------------------------------------------------------------------
% profile picture
\cvprofilepic{pics/profile}
% your name
\cvname{\LARGE Hugo MACHEFER}
% job title/career
\cvjobtitle{Full Stack Developer | Devops | Tech Lead }

% phone number
\cvphone{001 514 659 0718}
% email address
\cvmail{hugo.machefer@gmail.com}

\cvlinkedin{linkedin.com/in/hugomachefer}{hugomachefer}

\cvgithub{https://github.com/hmachefe}{hugomachefer}

% short address/location, use \newline if more than 1 line is required
\cvaddress{5563 avenue de Darlington, H3T1T1 Montréal}


% add additional information
% \newcommand{\additional}{some more?}


% add more profile sections to sidebar on first page
\addtofrontsidebar{
	% include gosquare national flags from https://github.com/gosquared/flags;
	% naming according to ISO 3166-1 alpha-2 country codes
	\graphicspath{{pics/flags/}}

	\profilesection{Skills}
    \chartlabel{Programmatic languages:}\\
      \pointskillNinety{}{TypeScript, JavaScript}
      \pointskillNinety{}{HTML (HTML 5)}
      \pointskillNinety{}{CSS (Css3, Css 3D)}
      \pointskillEighty{}{PHP (v7 et v5)}
      \pointskillSeventy{}{Python (v2 et v3)}
      \pointskillSixty{}{C\# (.NET Framework, Mono)}
      \pointskillForty{}{Java (Fx, Swing, Maven)}
      \pointskillForty{}{C/C++ (cross-compilation)}
      \pointskillForty{}{QT (4 and 5)}
    \chartlabel{Front-end (web):}\\
      \pointskillNinety{}{Angular (9/10/14)}
      \pointskillEighty{}{jQuery}
      \pointskillSeventy{}{React}
      \pointskillSeventy{}{RxJS / Observables}
      \pointskillSeventy{}{SCSS / SASS}
      \pointskillSixty{}{Bootstrap (Responsive)}
      \pointskillFifty{}{Backbone}
      \pointskillForty{}{VueJS}
      \pointskillThirty{}{ThreeJS (3D)}
    \chartlabel{Back-end:}\\
      \pointskillNinety{}{OpenAPI/Swagger (TSOA)}
      \pointskillSeventy{}{Express (Node.js)}
      \pointskillSixty{}{Microservices (in Python)}
      \pointskillSixty{}{Yii (PHP framework)}
      \pointskillThirty{}{Django (Python framework)}
      \pointskillThirty{}{Elixir (Robust scalability)}
      \pointskillTwenty{}{LaTeX: (Typesetting)}
    \chartlabel{Database:}\\
      \pointskillNinety{}{DynamoDB / (MongoDB)}
      \pointskillEighty{}{ElasticSearch}
      \pointskillSeventy{}{PostGres}
      \pointskillEighty{}{Sqlite (or MySql)}
      \pointskillForty{}{Microsoft SQL Server}
}


%-------------------------------------------------------------------------------
%                              SIDEBAR 2nd PAGE
%-------------------------------------------------------------------------------
\addtobacksidebar{
\vspace*{-6mm}  % Adjusts the vertical space, move content up by 10mm
\chartlabel{AWS Cloud:}\\
\pointskillNinety{}{EC2}
\pointskillNinety{}{S3}
\pointskillNinety{}{Lambdas (layer)}
\pointskillNinety{}{Secrets Manager}
\pointskillEighty{}{IAM}
\pointskillEighty{}{CloudFront (CDN)}
\pointskillEighty{}{CloudWatch}
\pointskillSeventy{}{Elastic Beanstalk}
\pointskillSeventy{}{ECR}
\pointskillSeventy{}{Step Functions}
\pointskillTwenty{}{Fargate (ECS)}
\pointskillEighty{}{Route53 (DNS)}
\pointskillEighty{}{Certificates (ACM)}

\chartlabel{Azure Cloud:}\\
\pointskillForty{}{Text To Speech Service}

\chartlabel{DevOps:}\\
\pointskillEighty{}{Terraform (IaC Multi-Cloud)}
\pointskillSeventy{}{Kubernetes (Orchestration)}
\pointskillFifty{}{CloudFormation (IaC AWS)}

\chartlabel{HTML5 players:}\\
\pointskillNinety{}{Bitmovin}
\pointskillNinety{}{Accurate Player (Codemill)}
\pointskillSeventy{}{Video.js (open source)}

\chartlabel{Multimedia:}\\
\pointskillNinety{}{FFMPEG}
\pointskillNinety{}{AWS MediaConvert}
\pointskillSeventy{}{Hybrik}

\chartlabel{Mobile Development:}\\
\pointskillSixty{}{Java Android (Dalvik)}
\pointskillForty{}{Ionic (Apache Cordova)}
\pointskillThirty{}{Xcode (Objective C)}


\chartlabel{Version Control Systems:}\\
\pointskillEighty{}{Git (gitlab, github)}
\pointskillForty{}{SVN / Synergy}

\chartlabel{Operating Systems:}\\
\pointskillEighty{}{Linux (Ubuntu 22)}
\pointskillSeventy{}{Windows (Win 10)}
\pointskillFifty{}{Mac (El Capitan 10.11.2)}

\chartlabel{IDE:}\\
\pointskillNinety{}{Webstorm (Jetbrains)}
\pointskillEighty{}{Visual Code Editor}
\pointskillSeventy{}{Vim / Vi}


\chartlabel{Agility:}\\
\pointskillEighty{}{Jira (backlog, sprint)}
\pointskillEighty{}{Confluence / wiki}
\pointskillEighty{}{Scrum (grooming, review)}
}

\addtothirdsidebar{
\vspace*{-6mm}  % Adjusts the vertical space, move content up by 10mm

  \chartlabel{Instant messaging:}\\
  \pointskillSeventy{}{Teams}
  \pointskillEighty{}{Slack}

  \chartlabel{UX / UI:}\\
  \pointskillSeventy{}{Figma}
  \pointskillSeventy{}{Miro}

  \chartlabel{AI:}\\
  \pointskillEighty{}{Chatgpt 4.0}
  \pointskillSixty{}{OpenAI API}

	\profilesection{Languages}
	\barskill{}{\textbf{French} (Mother Tongue)}{100}
	\barskill{}{\textbf{English} (TOEFL)}{95}
	\barskill{}{\textbf{German} (Educational, 2 years)}{35}
	\barskill{}{\textbf{Spanish} (Beginner, Duolingo)}{25}

	\profilesection{Interests}
		\skill{\faLaptop}{Ai, WebGl/VR/AR, streaming}
		\skill{\faFilm}{Movie, theather, cinema}
		\skill{\faGlobe}{International geopolitics}
		\skill{\faSwimmer}{Swimming, Basket-ball}

	\profilesection{Short Bio}
	\aboutme{
With over 26 years of experience in web development for digital TV, media platforms, and mobile devices, I have led the architecture, development, and deployment of two major Azure-based projects. My role involves collaborating with a team of developers and a QA specialist to enhance our software stack through module creation, code reviews, and the implementation of agile practices. I am passionate about innovating web solutions that are user-friendly and scalable, leveraging technologies like AWS, Angular, Vue.js, React, PHP, Python, HTML5, and AI.}\\
}

%-------------------------------------------------------------------------------
%                         TABLE ENTRIES RIGHT COLUMN
%-------------------------------------------------------------------------------
\begin{document}
% \sidebarwidth=0\paperwidth
% \newgeometry{right=1cm,left=1cm,bottom=0.1cm,top=1cm}

% \vskip30pt

% \begin{center}
%     {\color{cvblue} \Huge Cover Letter}
% \end{center}
% \vskip20pt

% {
% }


\newpage
\restoregeometry
\sidebarwidth=0.35\paperwidth

\makefrontsidebar

\cvsection{Working Experience}
\begin{cvtable}
    \cvitem{Aug, 2020 -- ongoing}{\color{cvsectioncolor}Senior Research Fellow}
    {\textbf{(Tech lead), Montreal}}
    {
      Working as a Senior Research Fellow in Soft Robotics at the University of Salford. Major research area includes control of pneumatic actuators and soft grippers.
    }

	\cvitem{Sep, 2016 -- ongoing}{\color{cvsectioncolor}Assistant Professor\quad (currently onleave)}{\textbf{Benha Univ., Egypt}}{Assistant Professor of Robotics Engineering at Electrical Engineering Department, Faculty of Engineering (Shoubra), Benha University. }

	\cvitem{Sep, 2018 -- Aug, 2019}{\color{cvsectioncolor}Adjunct Assistant Professor}{\textbf{E-JUST Univ., Egypt}}{Working as an Adjunct Assistant Professor for one day/week at Mechatronics and Robotics Engineering Department, Egypt-Japan University of Science and Technology (E-JUST), Egypt.}

	\cvitem{May, 2017 -- Jun, 2018}{\color{cvsectioncolor}Post-Doc Fellow}{\textbf{KOREATECH Univ., S. Korea}}{Worked on soft haptic for soft robots research and involved in a collaboration project with \href{http://charm.stanford.edu/}{CHARM Lab., Stanford University} with title “Human-Centered Design and Control of Vine Robots for Disaster Scenarios".}

	\cvitem{Oct, 2016 -- Feb, 2017}{\color{cvsectioncolor}Adjunct Assistant Professor}{\textbf{Zewail City Univ., Egypt}}{Worked as a part-time Adjunct Assistant Professor at Aerospace Engineering Department for two days/week. Delivering an undergraduate course (SPC 318: System Modeling and Linear Systems).}

	\cvitem{Sep, 2015 -- May, 2016}{\color{cvsectioncolor}Visiting Researcher}{\textbf{NAIST Univ., Japan}}{Conducted experiments with KUKA LWR iiwa R820 robot manipulator and doing research on eye-gaze input interface in HRI applications.}

	\cvitem{Jul, 2008 -- Sep, 2011}{\color{cvsectioncolor}Teaching Assistant}{\textbf{Benha Univ., Egypt}}{Worked as a full-time Teaching Assistant at the Electrical Engineering Department, Faculty of Engineeing (Shoubra), Benha University to help in teaching courses in electronics and robotics subjects.}

	\cvitem{Jul, 2008 -- Sep, 2011}{\color{cvsectioncolor}Embedded Systems Engineer}{\textbf{Egytronix Co., Egypt}}{Worked as a part-time embedded systems engineer (four days/week) in the field of power electronics applications and embedded systems design.}
\end{cvtable}


\cvsection{Education}
\subsection{Postgraduate Studies}
\begin{cvtable}
	\cvitem{2013 -- 2016}{\color{cvsectioncolor}Ph.D. in Mechatronics and Robotics Engineering}{\href{www.ejust.edu.eg}{\textbf{E-JUST, Egypt}}}
		{\textbf{Title}: Development of a Cognitive Human-Robot Interaction System for Dexterous Teleoperation.\\
		\textbf{Supervisors}: Prof. Said Megahed, Dr. Samy Assal, Prof. Ahmed A. Abouelsoud and Prof. Tsukasa Ogasawara.\\
		\textbf{Grade: }CGPA: 3.78\\
		\chartlabel{HRI} \chartlabel{Teleoperation} \chartlabel{Shared Control} \chartlabel{Eye Gaze}}

	\cvitem{2011 -- 2013}{\color{cvsectioncolor}M.Sc. in Mechatronics and Robotics Engineering}{\href{www.ejust.edu.eg}{\textbf{E-JUST, Egypt}}}
		{\textbf{Title}: Improving Robots Exploration by Heuristic Backtracking in Sensor-based Techniques.\\
		\textbf{Supervisors}: Dr. M. Abdellatif and Dr. Samy Assal\\
		\textbf{Grade: }CGPA: 3.5\\
	\chartlabel{Mobile Robots} \chartlabel{Exploration} \chartlabel{Navigation} \chartlabel{Path Planning}}
\end{cvtable}


\subsection{Undergraduate Study}
\begin{cvtable}
\cvitem{2002 -- 2007}{\color{cvsectioncolor}\small B.Sc. in Electronics and Communications Engineering}{\href{http://bu.edu.eg/en/}{\textbf{Benha Univ., Egypt}}}
		{\textbf{Prject Title}: A Mototrized Wheelchair for Handicapped.\\
		\textbf{Supervisors}: Dr. Asharaf Hafez\\
		\textbf{Grade: } Very Good (Ranked 3rd. among 200 students)}
	\end{cvtable}

\subsection{Other Training}
\begin{cvtable}
\cvitem{May 2005}{\color{cvsectioncolor}\small Embedded Systems Diploma}{\textbf{Jelecom Co., Egypt}}
		{Training on microcontrollers: 8051, AVR, PIC and Motorola.}
	\end{cvtable}

% 	Ph.D. Theses: (Two students)
% { . (2018 - 2020)
% {  (2018 - 2020)
% M.Sc. Theses: (Two students)
% { An Intutive Input Interface for teloperation of a Multi-section Continuum Robot. (2019-2021)
% {  (2019-2021)
\newpage
\makebacksidebar
\cvsection{Teaching Experience}
\subsection{Postgraduate Courses}
\begin{cvtable}
	\cvitem{E-JUST University}{MTR 601: Intelligent Control Systems}{Fall'18, Spring'19}{Fuzzy Logic Control, Neural Network Control, Evolutionary Algorithms and Genetic Programming.}
	\cvitem{Benha University}{ECE 501: Advanced Embedded Systems}{Fall'16}{Micro-controllers and Microprocessors Applications}
% 	\cvitem{Benha University}{ECE 447: Robotics Engineering}{Spring'17, Spring'19}{Robot Structure, Kinematics, Dynamic and Control.}
% 	\cvitem{}{ECE 447: Robotics Engineering}{Spring'17, Spring'19}{Robot Structure, Kinematics, Dynamic and Control.}
\end{cvtable}

\subsection{Undergradute Courses}
\begin{cvtable}
\cvitem{Benha University}{ECE 447: Robotics Engineering}{Spring'17, Spring'19}{Robot Structure, Kinematics, Dynamics and Control.}
\cvitem{}{ECE 101: Electronics (I)}{Fall'16}{Basic of Electronics: PN Junctions, Diode applications.}
\cvitem{}{ECE 102: Electronics (II)}{Spring'17}{LEDs, Optocouplers, Photodiodes and applications.}
\cvitem{}{ECE 204: Electrical and Electronic Measurements}{Fall'16, Fall'18}{PMMC, Avometers, Digital Instruments, Sensor and actuators.}
\cvitem{ZewailCity University}{SPC 318: System Modeling and Linear Systems}{Fall'18}{Transfer function, State-Space, First and Second Order Systems, Stability Analysis and Root Locus.}
\cvitem{YouTube}{\href{https://www.youtube.com/playlist?list=PL_rxK_FJ4p0agYcYRZwa9mbMUvnhesZ4v}{\textbf{Introduction to \LaTeX\, in Arabic}}}{Since Dec 8, 2014}{}
	\end{cvtable}

\cvsection{Academic Supervision}
\begin{cvtable}
	\cvitem{2018--2020}{\small Demonstration-Guided Motion Planning for Continuum Robots}{Ph.D.}{}
	\cvitem{2018--2020}{\small Intelligent Control of Automotive Air-Spring Suspension System.}{Ph.D.}{}
	\cvitem{2019--2020}{\small Intuitive teloperation of Multi-section Continuum Robots.}{M.Sc.}{}
	\cvitem{2019--2020}{\small Autonomous Tasks-around-head Assistance for Patients with Movement Disabilities}{M.Sc.}{}
\end{cvtable}

\cvsection{Honours and Awards}
\begin{cvtable}
	\cvitem{May 2018}{Award of Research Excellence (10000 EGP)}{Benha Univ., Egypt}{}
		\cvitem{Jan 2017}{Award of Research Excellence (4000 EGP)}{Benha Univ., Egypt}{}
		\cvitem{Sep 2011}{Awarded M.Sc. and Ph.D. Scholarships}{MoHE, Egypt}{}
\end{cvtable}


\cvsection{Invited Talks}
\begin{cvtable}
	\cvitem{Mar 2019}{Entrepreneur Workshop}{E-JUST Univ.}{Gave a two hours lecture on career support and entrepreneurships.}
		\cvitem{May 2009}{Getting Started in Embedded Systems}{Benha Univ.}{Gave a lecture on getting started in embedded systems.}
\end{cvtable}
\section{Review Duties}
\begin{cvtable}
	\cvitem{Journals}{Advanced Robotics, Intelligent Service Robots.}{}{}
	\cvitem{Conferences}{ICRA’17, IROS’18, ICRA’19, ICAR'19.}{}{}
\end{cvtable}

\cvsection{References}
\begin{cvtable}
	\cvitem{Ref. 1}{Prof. XXX CCCC}{EE Univ., Egypt}{xxx[dot]yyy[at]ddd[dot]edu[dot]eg}
			\cvitem{Ref. 2}{Prof. XXX CCCC}{EE Univ., Egypt}{xxx[dot]yyy[at]ddd[dot]edu[dot]eg}
	\cvitem{Ref. 3}{Prof. XXX CCCC}{EE Univ., Egypt}{xxx[dot]yyy[at]ddd[dot]edu[dot]eg}

\end{cvtable}

\newpage
\makethirdsidebar

\cvsection{Publications}
\subsection{Journals}
	\begin{itemize}
	{\small
	\item mmm}
\end{itemize}
\vskip20pt
 \subsection{Conferences}
\begin{itemize}
{\small
\item ccc}
		\end{itemize}


\end{document}
